---
title: "Extortion in Mexico: Basic EDA of several sweeps of the ENVE"
author: "Patricio R. Estevez Soto"
email: "patricio.estevez.14@ucl.ac.uk"
date: "21/09/2017"
output:
    md_document:
    variant: "markdown"
pandoc_args: "--smart"
---

# Set up, data input and pre-process

## Session info

We first check details of the session and system, and for reproducibility, we set the random seed.

```{r session, cache=FALSE}
starttime <- proc.time()
date()
sessionInfo()
set.seed(42)
options(scipen=0)
```

## Load packages and functions

Install custom package, requires `devtools`.

```{r install-victim}
# devtools::install_github("prestevez/victim")
```

Next we load the packages that we will use.

```{r packages}

# check.packages function: install and load multiple R packages.
# Check to see if packages are installed. Install them if they are not, then load them into the R session.
check.packages <- function(pkg){
    new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
    if (length(new.pkg))
        install.packages(new.pkg, dependencies = TRUE,
            repos = "https://cloud.r-project.org")
    sapply(pkg, require, character.only = TRUE)
}

check.packages("devtools")

install_version("foreign", version = ‘0.8.67’,
    repos = "https://cloud.r-project.org")

library(foreign)

sessionInfo()
getwd()
list.files()
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment="",
                      cache=TRUE,
                      dev=c("png", "CairoPDF"),
                      error=TRUE,
                      fig.width=5, fig.height=4)
options(knitr.kable.NA = '--')
```


## Data description  

Se asume que los nombres de las tablas de datos son los siguientes:


- Enve 2012
    - Principal: `enve2012cuest_ciega_2012.dbf`
    - Delitos: `enve2012delitos_ciega_2012.dbf`
- Enve 2014
    - Principal: `enve2014cuest_ciega_2014.dbf`
    - Delitos: `enve2014delitos_ciega_2014.dbf`
- Enve 2016
    - Principal: `enve2016cuest_ciega_2016.dbf`
    - Delitos: `enve2016delitos_ciega_2016.dbf`

Si fueran diferentes se ruega se adapten los nombres en el bloque de codigo a continuacion.

```{r 2014-import-data}
enve_2012 <- read.dbf("enve2012cuest_ciega_2012.dbf")
summary(enve_2012)

enve_delitos_2012 <- read.dbf("enve2012delitos_ciega_2012.dbf")
summary(enve_delitos_2012)

enve_2014 <- read.dbf("enve2014cuest_ciega_2014.dbf")
summary(enve_2014)

enve_delitos_2014 <- read.dbf("enve2014delitos_ciega_2014.dbf")
summary(enve_delitos_2014)

enve_2016 <- read.dbf("enve2016cuest_ciega_2016.dbf")
summary(enve_2016)

enve_delitos_2016 <- read.dbf("enve2016delitos_ciega_2016.dbf")
summary(enve_delitos_2016)

```

END
